How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-06-29 Paper/paper.tex
Changed style to sig-alternate-05-2015 for camera ready

\documentclass{sig-alternate}

@@

@@

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{terms}

\keywords{Scratch, block-based languages, programming practices, code smells, static analysis}

@@

The second smell that we examine is the dead code smell. We identify four types of dead code: (1) procedures that are not invoked, (2) unmatched broadcast-receive messages, (3) code that is not invoked and (4) empty event scripts. Investigating the first type, we find that a significant number of the defined procedures (13,036 or 5.06\%) are not called in the projects. This is also shown in Figure \ref{fig:procedurecalls} and it occurs in 2,079 projects. For the second type, we examined the broadcast-receive messages and found that they are not always synchronized: 3,33\% of the \texttt{when I receive} blocks were found to wait for a message that is never being broadcasted, while 4,4\% of the \texttt{broadcast} blocks broadcast a message that is not being received. This lack of syncronization occurs in 18,669 (7.99\% of the total) projects.

@@

Large-scale analyses of Scratch projects have been performed using the dataset made available by the Lifelong Kindergarten Group at the MIT Media Lab, which contains data for Scratch projects created until 2012, when the web-based programming environment was introduced. In \cite{yang_2015}, this dataset was used for exploring the learning patterns of users in terms of block use over their first 50 projects. Dasgupta \emph{et al.} investigated how project remixing relates to the adoption of computational thinking concepts \cite{Dasgupta_2016}. In \cite{fields_2014}, the use of programming concepts was examined in relation to the level of participation (commenting, remixing, etc), the gender, and the account age of 5,000 Scratch programmers.

@@

In addition to the findings presented in this paper, we provide as contributions the dataset that we used for our study, as well as information on the edge cases that we found in the dataset in terms of size and number of procedures, variables, cyclomatic complexity, clones and dead code.\footnotemark[\ref{repo}]

>>>>

\documentclass{sig-alternate-05-2015}

@@

% Copyright
\CopyrightYear{2016} 
\setcopyright{othergov}
\conferenceinfo{ICER '16,}{September 08-12, 2016, Melbourne, VIC, Australia}
\isbn{978-1-4503-4449-4/16/09}\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/2960310.2960325}

\clubpenalty=10000 
\widowpenalty = 10000

@@

\keywords{Scratch; block-based languages; programming practices; code smells; static analysis}

@@

The second smell that we examine is the dead code smell. We identify four types of dead code: (1) procedures that are not invoked, (2) unmatched broadcast-receive messages, (3) code that is not invoked and (4) empty event scripts, i.e., scripts that contain an event block alone. Investigating the first type, we find that a significant number of the defined procedures (13,036 or 5.06\%) are not called in the projects. This is also shown in Figure \ref{fig:procedurecalls} and it occurs in 2,079 projects. For the second type, we examined the broadcast-receive messages and found that they are not always synchronized: 3,33\% of the \texttt{when I receive} blocks were found to wait for a message that is never being broadcasted, while 4,4\% of the \texttt{broadcast} blocks broadcast a message that is not being received. This lack of syncronization occurs in 18,669 (7.99\% of the total) projects.

@@

Large-scale analyses of Scratch projects have been performed using the dataset made available by the Lifelong Kindergarten Group at the MIT Media Lab, which contains data for Scratch projects created until 2012, when the web-based programming environment was introduced. In \cite{yang_2015}, this dataset was used for exploring the learning patterns of programmers in terms of block use over their first 50 projects. Dasgupta \emph{et al.} investigated how project remixing relates to the adoption of computational thinking concepts \cite{Dasgupta_2016}. In \cite{fields_2014}, the use of programming concepts was examined in relation to the level of participation (commenting, remixing, etc), the gender, and the account age of 5,000 Scratch programmers.

@@

In addition to the findings presented in this paper, we provide as contributions the dataset that we used for our study, as well as the project identifiers and information on the edge cases that we found in the dataset in terms of size and number of procedures, variables, cyclomatic complexity, clones and dead code.\footnotemark[\ref{repo}]
